Does pre-crastination explain why some observers are sub-optimal in a visual search task?

### 2023-09-04 RegReport/paper.tex
Update paper.tex

We now investigate whether our data suggests any new hypotheses that could be of interest to other researchers. We find some tentative evidence to suggest that participants who do not pre-crastinate may score slightly higher in extraversion and open-mindedness. We find no evidence of any clear relationships between the personality measures and visual search strategy.

@@

\subsubsection{Personality and Visual Search Strategy}

\subsubsection{Personality and Pre-crastination}

@@

In addition to the registered measures, for efficiency we collected a range of other demographic characteristics and free-report measures from our participants. These are outside the scope of the pre-registration we have presented in this paper, so a full exploration of these additional variables and their relationship to visual search and precrastination will be presented elsewhere. In the interest of open science, however, and to avoid possible confusion by separating or duplicating data, the full set of data analysed in this pre-registration is presented along with these additional variables here: [link to data]. We request anyone wanting to use the data in this repository to contact the corresponding author and to reference... what? this paper? We'll need to write up a brief report about the data and submit it so people have something to reference. Maybe Anna could make a start on this??

\section{General Discussion}
Although the smaller pilot sample (N=30) suggested participants who pre-crastinate tended to use their peripheral vision to search more efficiently, the larger sample (N=201) did not support that conclusion. While this is a null finding, it is nonetheless meaningful because we had a clear prediction based on data and theory and designed a robust experiment to test it. We replicated the previously-established patterns in finding (1) a good split of people who consistently pre-crastinated and people who consistently did not and (2) a broad range of individual differences in visual search efficiency. If a stable relationship between these factors exists and is large enough to build any theories around, this experiment would have detected it. The fact that it did not detect it is useful in ruling out explanations for either behaviour (precrastination or visual search inefficiency) that is grounded in a shared personality characteristic like conscientiousness or impulsivity.

What did we learn?
The relationship between conscientiousness and pre-crastination observed previously was not observed here. We did have a rather conscientious sample though.
Possible relationships between procrastination and pre-crastiation is interesting and was also not observed previously.
People's reports of what they say they are doing / how they justify their choices is interesting and future research can explore these.
We have a rich dataset here with many other measures and we invite others to use it in hypothesis-generating exploratory analyses of their choosing.

>>>>

We now investigate whether our data suggests any new hypotheses that could be of interest to other researchers.

@@

\subsubsection{Personality and Pre-crastination}
The left column of Figure \ref{fig:exp_analysis} shows the relationship between 10 personality measures and precrastination in a sample of 304 participants. The width of the bar is the range of the $95\%$ CI around the difference between precrastinators and non-precastinators on each measure. Most measures are close to 0 (the vertical dashed line). We find some tentative evidence to suggest that participants who pre-crastinate may score slightly higher in impulsivity and lower in extraversion and open-mindedness. We did not make any specific predictions about these personality measures, and so we refrain from interpreting these, but report them here for the benefit of future research (with the caution that if the effect size estimates based on a sample of such a large size are close to 0, they will be diffiult to detect).

\subsubsection{Personality and Visual Search Strategy}
The right column of Figure \ref{fig:exp_analysis} shows the relationship between 10 personality measures and visual search strategies, expressed as a correlation between effiency score (proportion of fixations on the heterogeneous side) and score on each scale/subscale.  We find no evidence of any clear relationships between the personality measures and visual search strategy in this sample of 201 participants.

@@

In addition to the registered measures, for efficiency we collected a range of other demographic characteristics and free-report measures from our participants. These are outside the scope of the pre-registration we have presented in this paper, so a full exploration of these additional variables and their relationship to visual search and precrastination will be presented elsewhere. In the interest of open science, however, and to avoid possible confusion by separating or duplicating data, the full set of data analysed in this pre-registration is presented along with these additional variables here: [link to data].

\section{General Discussion}
Although the smaller pilot sample (N=30) suggested participants who pre-crastinate tended to use their peripheral vision to search more efficiently, the larger sample (N=201) did not support that conclusion. While this is a null finding, it is nonetheless meaningful because we had a clear prediction based on data and theory and designed a robust experiment to test it, which underwent rigourous peer review. Both the pilot and the final experiment replicated the previously-established patterns in finding (1) a good split of people who consistently pre-crastinated and people who consistently did not and (2) a broad range of individual differences in visual search efficiency. If a stable relationship between these factors exists and is large enough to build any theories around, this experiment would have detected it. The fact that it did not detect it is useful in ruling out explanations for either behaviour (precrastination or visual search inefficiency) that is grounded in a shared personality characteristic like conscientiousness or impulsivity.

The relationship between conscientiousness and pre-crastination observed previously \cite{sauerberger2019} was not observed here. This could be because the original effect was a statistical accident, or because the effect is small and not present in our sample. One point to note is that our sample was skewed towards the higher end of the conscientiousness scale, likely because unconscientious people are less inclined to participate in psychology experiments. It is possible that the sample in \cite{sauerberger2019} was more representative of the full range of conscientiousness in the population, and was therefore more sensitive to the relationship with precrastination. On the other hand, one might expect our more conscientious sample would have higher precrastination rates than previously observed, and this was not the case. Another interesting and counterintuitive observation from \cite{sauerberger2019} was that procrastination was unrelated to precrastination, and the current results show a small negative correlation, as one would expect if starting tasks too soon is predictive of not starting tasks too late. Overall, we have a rich dataset here with many other measures and we invite others to use it in hypothesis-generating exploratory analyses of their choosing. We request that anyone using the data in this repository reference this paper.
